Explore Local Memory Design for Building Hypervisor on Resource Disaggregated Architecture

### 2019-11-04 paper.tex
Add implementation.

@@

>>>>

% Figure for page fault handling
\begin{figure*}[h!]
     \centering
     \includegraphics[width=\linewidth,height=.3\textheight]{figures/page_fault_flow.png}
     \caption{Page fault flow to simulate remote memory and remote storage access.}
     \label{fig:page fault flow}
\end{figure*}

@@

We implement our simulation framework by extending Xen hypervisor. The key is how to manipulate page table and page fault correctly to correctly simulate the behavior of local and remote menry of disaggregated architecture. Before going to the implementation details, we descripe some terminologies related to address translation that will show in the following article.

\subsection{Address Translation in a Virtualized Environment}
In a virtualized environment, there are three software layers: guest applications, guest OSes, and hypervisor. There are also three address spaces: guest virtual address (GVA), guest physical address (GPA), and machine physical address (MPA). GVA is the address issued by executing guest applications and guest OSes. And the guest's page table will translate the GVA into GPA. While in a non-virtualized environment, the GPA is actually the final physical address and is valid to be used to access memory. In a virtualized environment, on the other hand, the GPA needs a further translate into MPA and then is able to access the memory. The translation from GPA to MPA is handed by page table maintained by hypervisor.

\subsection{Simulating Local/Remote Memory}
The key idea is to separate main memory of a server into local and remote memory region. It's worthy to noting that the region separation are from the MPA's viewpoint. Guest applications and OSes are allowed to access the local memory region, otherwise a page fault comes. If local memory is not enough, a page in the local memory region is evicted into remote memory region such that a memory request can be made to local memory region. In the local page eviction process, the correspond page table entry (PTE) is updated to point the remote memory region and is marked unreadable to cause further page fault. Corresponding TLB is flushed to assure correctness.

The detailed page fault flow is depicted in Fig \ref{fig: page fault flow}. When a page fault happens, this implies that a remote memory is accessed. We do a wait in the fault handler to simulate the remote memory access latency. If the page is not in the remote memory region, a storage access is made, and incurs a wait to simulate remote storage access. Either the page in remote memory region or need a storage, the data will end up being cached in the remote memory region. Then the page is copied to local region and followed by a PTE updated to make future access hit the page in local memory region as well a TLB flush. Similar as previous paragraph described, if a page eviction happens, it comes with a PTE update and TLB flushed for that victim page.
